---
title: "p8105_hw6_js5095"
author: Jianting Shi
date: 2020-12-09
output: github_document
---

```{r}
library(tidyverse)
library(MASS)
library(modelr)
library(rnoaa)
```


# Problem 2

### Load and clean the data for regression analysis

```{r}
# Load data and clean
bw_df = 
  read_csv("./data/birthweight.csv")%>%
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         frace=as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))
```

### Propose a regression model for birthweight on a data-driven model-building process

```{r}
# Use step-wise model selection to provide a data-driven model
full_model = lm(bwt ~., bw_df)
step_model = stepAIC(full_model,
                     direction = "both",
                     trace = FALSE)

#summary(step_model)

#formula(step_model)

#step_model %>% broom::tidy()

# Add predictions and residuals
bw_df = bw_df %>%
  modelr::add_predictions(step_model) %>% 
  modelr::add_residuals(step_model)
```

Describe your modeling process：
I applied a classic method, stepwise regression, to identify the optimal linear model from a collection of predictors. I started with the full model (using all variables as predictors), and instructed the algorithm to apply stepwise regression based on AIC. The resulting model has 13 predictors.

### Create a plot of model residuals against fitted values

```{r}
# Create residuals & prediction plots
bw_df %>%
  ggplot(aes(x = resid, y = pred)) + geom_point()
```
Describe the plots:
The predictions center around 3000, whereas the residuals center around 0. There are a few outliers in prediction, as the predicted birthweights are negative.

### Make comparison with two other models in terms of the cross-validated prediction error

```{r}
# Create two other models
model_1 = lm(bwt ~ blength + gaweeks, data=bw_df)
model_2 = lm(bwt ~ bhead*blength*babysex, data=bw_df )

# Cross validation
set.seed(345)
cv_bw_df = 
  crossv_mc(bw_df, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_bw_df = 
  cv_bw_df %>%
  mutate(
    step_mod = map(train, ~lm(formula(step_model), data=.x)),
    model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data=.x)),
    model_2 = map(train, ~lm(bwt ~ bhead*blength*babysex, data=.x))
  ) %>%
  mutate(
    rmse_step_mode = map2_dbl(step_mod, test, ~rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
  )
  
# RMSE plot 
cv_bw_df %>% 
  dplyr::select(starts_with("rmse_")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
Through comparison by cross validation, the model derived from stepwise regression has the lowest variance in prediction error across three different models. The model 2(head circumference, length, sex, and all interactions) also has a lower variance in prediction error.

# Problem 3

```{r}
# Load data
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  dplyr::select(name, id, everything())
```

```{r}
# Bootstrap DB
set.seed(567)
weather_df_bs = 
  weather_df %>%
  modelr::bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result_term = map(models, coef),
    result_all = map(models, broom::glance)
  ) %>%
  unnest(result_all) %>%
  mutate(
    result_term = map(result_term, toString)) %>%
  separate(result_term, sep = ", ", into=c("beta_0", "beta_1"), convert = T) %>%
  mutate(log_beta = log(beta_0*beta_1)) %>%
  dplyr::select(-strap, -models)
```


```{r}
# Plot density
weather_df_bs %>%
  ggplot(aes(x = r.squared)) + geom_density()

weather_df_bs %>%
  ggplot(aes(x = log_beta)) + geom_density()
```
In the first plot, r.squared has a shoulder on the left; In the second plot, log_beta has a more symmetric, gausian-like distribution.

```{r}
# Empirical 95% CI
r_square_95CI = c(quantile(weather_df_bs$r.squared, probs = 0.025),
                  quantile(weather_df_bs$r.squared, probs = 0.975))

r_square_95CI

log_beta_95CI = c(quantile(weather_df_bs$log_beta, probs = 0.025),
                  quantile(weather_df_bs$log_beta, probs = 0.975))

log_beta_95CI

```

The 95% CI for r.squared is (0.89, 0.93);\
The 95% CI for log_beta is (1.96, 2.05).

